API design for machine learning software: experiences from the scikit-learn project

### 2013-10-19 paper.tex
Don't cite mini-batch k-means
Indeed, we do not cite any of the other mentioned algorithms. I don't think we should make an exception for this one.

Finally, the Gensim topic modeling toolkit \citep{rehurek2010gensim}
exemplifies an API geared toward ``big data'' processing.
Gensim's method of dealing with large datasets is to use algorithms
that have small space complexity and can be updated online.
The API is designed around the Python concept of an ``iterable''
(supported in the language by a restricted form of co-routines called generators).
Some \sklearn estimators, among others the implementations of naïve Bayes
and minibatch $k$-means \citep{sculley2010web},
have a \texttt{partial\_fit} method to learn from a stream of samples
that is divided into mini-batches (chunks).
This way of processing, as argued in Section~\ref{sec:arrays},
allows for more efficient implementation.
We make no attempt to hide this batch-oriented processing from the user,
allowing control over the amount of memory dedicated to \sklearn algorithms.

>>>>

Finally, the Gensim topic modeling toolkit \citep{rehurek2010gensim}
exemplifies an API geared toward ``big data'' processing.
Gensim's method of dealing with large datasets is to use algorithms
that have small space complexity and can be updated online.
The API is designed around the Python concept of an ``iterable''
(supported in the language by a restricted form of co-routines called generators).
Some \sklearn estimators, among others the implementations of naïve Bayes
and minibatch $k$-means,
have a \texttt{partial\_fit} method to learn from a stream of samples
that is divided into mini-batches (chunks).
This way of processing, as argued in Section~\ref{sec:arrays},
allows for more efficient implementation.
We make no attempt to hide this batch-oriented processing from the user,
allowing control over the amount of memory dedicated to \sklearn algorithms.
